---
title: "Autonomy-level trade-off (AL0-AL5)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Autonomy-level trade-off (AL0-AL5)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-heller/dynasimR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-heller/dynasimR/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/r-heller/dynasimR/actions/workflows/pkgdown.yaml/badge.svg)](https://r-heller.github.io/dynasimR/)
[![CRAN status](https://www.r-pkg.org/badges/version/dynasimR)](https://CRAN.R-project.org/package=dynasimR)
[![Codecov test coverage](https://codecov.io/gh/r-heller/dynasimR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-heller/dynasimR?branch=main)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/dynasimR)](https://cran.r-project.org/package=dynasimR)
[![CRAN downloads total](https://cranlogs.r-pkg.org/badges/grand-total/dynasimR)](https://cran.r-project.org/package=dynasimR)
[![License: MIT](https://img.shields.io/badge/license-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>",
  fig.width = 6, fig.height = 4
)
```

```{r}
library(dynasimR)
sim <- load_example_data()
```

## AL-Efficiency ratio

We trade off event-rate reduction versus the Compliance Index. The
default AL scenario mapping requires the full sweep; here we
demonstrate with the two AL points in the shipped example data.

```{r}
al <- al_efficiency(
  sim,
  al_scenarios         = c("0" = "A-S00", "1" = "A-S01"),
  compliance_threshold = 0.80,
  n_bootstrap          = 200
)
al$tradeoff_table
```

## Trade-off plot

```{r}
plot_al_tradeoff(al)
```

## Interpretation

The `optimal_al` slot holds the AL level with the highest event-rate
reduction while staying above the compliance threshold:

```{r}
al$optimal_al
```

Compliance violations (if any):

```{r}
al$compliance_violations
```
