---
title: "Getting started with dynasimR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with dynasimR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width = 6, fig.height = 4
)
```

```{r}
library(dynasimR)
```

## Load data

```{r}
sim <- load_example_data()
print(sim)
```

## Time-to-event analysis

```{r}
km <- km_estimate(sim, endpoint = "stage2",
                  stratify_by = "scenario")
plot_km(km, title = "Time-to-stage-2")
```

## Policy effect

```{r}
pol <- policy_effect(sim,
  policy_a_scenario = "A-S08",
  policy_b_scenario = "A-S07",
  n_bootstrap       = 200)
cat(pol$narrative)
```

## Autonomy trade-off

Only two AL points are present in the shipped example data, but the
machinery is the same for a full AL sweep.

```{r}
al <- al_efficiency(
  sim,
  al_scenarios         = c("0" = "A-S00", "1" = "A-S01"),
  compliance_threshold = 0.80,
  n_bootstrap          = 200
)
plot_al_tradeoff(al)
```

## Manuscript-ready export

```{r, eval = FALSE}
export_latex_table(
  data     = pol$effect_sizes,
  filename = "policy_table.tex",
  caption  = "Policy effect sizes.",
  label    = "policy"
)
```

## Launching the dashboard

```{r, eval = FALSE}
launch_app()                                        # example data
launch_app(data_dir = "~/my-simulation/data/raw")
```

# Use of LLM tools

Portions of this package were prepared with assistance from large language model tooling for
narrowly defined, non-authorial tasks: copyediting, prose smoothing, Markdown/LaTeX formatting,
scaffolding of boilerplate files (CI configs, build scripts), code refactoring. The tools used were [Chat AI](https://kisski.gwdg.de/leistungen/2-02-llm-service/),
the LLM service of KISSKI (GWDG), and a self-hosted **Mistral Small (24B, Apache-2.0)** run locally via
[Ollama](https://ollama.com/) and the `ollamar` R package — local inference only, with no data sent to
third parties for the self-hosted model.

All scientific claims, methodological choices, analyses, interpretations, and conclusions are the
author's own. No LLM-generated text was incorporated without review and revision, and every reference
was verified against its DOI, arXiv ID, or ISBN.
